Eco-evolutionary model of salmon straying in a metapopulation (but with a cool title)

### 2017-05-12 Manuscript/msv1.tex
phenotypic divergence para

>>>>

%Lowering Phenotypic diversity with increasing straying rate
As expected, increasing rates of straying lowers phenotypic diversity because both local and remote populations become homogenized.
The sensitivity of this phenotypic homogenization to straying rate is increased with lower heritability because the selective forces acting against trait means far from local optima is lessened for lower $h^2$.
[A DISCRETE JUMP TO LOW DIVERSITY FOR LOW HERITABILTIY](Fig. \ref{fig:traitdiff}).

\begin{figure}
\centering
\includegraphics[width=0.4\textwidth]{figs/fig_traitdiff.pdf}
\caption{
} \label{fig:traitdiff}
\end{figure}
